---
title: "Ketagrids"
author: "Simon"
date: '2023-08-14'
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse,viridis,brms)

# helper function that requires to run brms model only once
modelpath = './brmsModels/'

run_model <- function(expr, modelName, path=modelpath, reuse = TRUE) {
  path <- paste0(path,'/', modelName, ".brm")
  if (reuse) {
    fit <- suppressWarnings(try(readRDS(path), silent = TRUE))
  }
  if (is(fit, "try-error")) {
    fit <- eval(expr)
    saveRDS(fit, file = path)
  }
  fit
}
```

## Read data

Here i load the individual files, and parse the data into a long format.

```{r}
#script for reading individual jsons
source("dataProcessing.R")
data_file_path<-"data/gridSearch01_06_Vienna/"

dat<-list.files(path = data_file_path)%>%
  purrr::map_dfr(.,~{dataImport_Adolescent(dataFile =paste0(data_file_path,.))})%>%
  mutate(z=z/50,#normalize rewards and previous rewards
         previous_reward=previous_reward/50)
```

# Unblinding.
For unblinding we need to replace session with whether people were on ketamine or not.

# Average reward across sections.

Now, i can already look at the data. First thing of interest is whether participants change their behavior across sessions.

It looks like there is a training effect such as that participants in session 2 were better overall.

```{r pressure, echo=FALSE}
#replace session with treatment
dReward = ddply(subset(dat, trial!=0), ~id+session, plyr::summarize, meanReward=mean(z))

pReward = ggplot(dReward, aes(x=as.factor(session), y=meanReward)) +
  geom_boxplot(color='black', outlier.shape = NA, width=.5) +
  geom_point(position = position_dodge2(0.05))+
  geom_line(aes(group=id),alpha=0.1,position = position_dodge2(0.05))+
  xlab('Session') +
  ylab('Normalized Mean Reward') +
  ggtitle('Performance') +
  theme_classic()
pReward
```

# Learning curves.

Learning seems to be more prolonged in session 2, so that participants get greater rewards in the later half of the experiment. 

```{r}
# Learning curves per age group - mean reward
dLearningCurves <- ddply(dat, ~id+trial+session, plyr::summarize, meanReward = mean(z))

pLearningCurves <- ggplot(dLearningCurves, aes(x=trial, y=meanReward, color=as.factor(session), group=session,fill=as.factor(session)))+
  stat_summary(fun.y = mean, geom='line', size=.5)+
  stat_summary(fun.data = mean_cl_boot, geom='ribbon', alpha=0.3, color=NA)+
  geom_hline(yintercept=0.5, linetype='dashed', color='red') + # random choice model
  #coord_cartesian(ylim = c(.45, 1.)) +
  xlab('Trial')+
  ylab('Normalized Reward ± 95% CI')+
  labs(color='Session') +
  labs(fill='Session') +
  ggtitle('Mean Reward') +
  theme_classic() +
  theme(strip.background=element_blank())

pLearningCurves
```
# Distance between search decisions

```{r}
DistancePrevReward = run_model(brm(distance ~ previous_reward * session + (previous_reward + session | id),
                                   data = dat, cores = 4, iter = 4000, warmup = 1000,
                                   control = list(adapt_delta = 0.99)), modelName = 'DistancePrevReward_sessions')
```

```{r}

# generate predictions
prevReward = seq(0,50) / 50 # normalized reward
newdat = expand.grid(previous_reward=prevReward, session=c(1,2))
# predict distance based on previous reward
preds = fitted(DistancePrevReward, re_formula=NA, newdata=newdat, probs=c(.025, .975))
predsDF = data.frame(previous_reward=rep(prevReward, 7),
                     agegroup=rep(levels(d$agegroup), each=length(prevReward)),
                     distance=preds[,1],
                     lower=preds[,3],
                     upper=preds[,4])

# average distance
grid = expand.grid(x1=0:7, x2=0:7, y1=0:7, y2=0:7)
grid$distance = NA

for(i in 1:dim(grid)[1]){
  grid$distance[i] <- dist(rbind(c(grid$x1[i], grid$x2[i]), c(grid$y1[i], grid$y2[i])), method = "manhattan")
}

meanDist = mean(grid$distance)

# plot predictions
pDistRewardRegression <- ggplot()+
  stat_summary(d, mapping=aes(x=previous_reward, y=distance, color=agegroup, fill=agegroup), fun.y=mean, geom='point', alpha=0.7, size=.5)+
  geom_line(predsDF, mapping=aes(x=previous_reward, y=distance, color=agegroup), size=.3) +
  geom_ribbon(predsDF, mapping=aes(x=previous_reward, y=distance, ymin=lower, ymax=upper, fill=agegroup), alpha=.3) +
  geom_hline(yintercept=meanDist, linetype='dashed', color='red') + # mean distance
  xlab('Normalized Previous Reward')+
  ylab('Distance to Next Option')+
  scale_color_viridis(discrete=TRUE, name='Age Group', direction=1) +
  scale_fill_viridis(discrete=TRUE, name='Age Group', direction=1) +
  ggtitle('Search Distance ~ Reward') +
  theme_classic() +
  theme(strip.background=element_blank(), legend.position='none')+
  facet_wrap(. ~ round)

pDistRewardRegression
# ggsave(filename = "plots/distReward.png", plot=pDistRewardRegression, height=2.5, width=4, units = "in")
d$distance

# plot model coefficients
set_theme(geom.label.color = 'black', base = theme_classic())

pCoeffs = sjPlot::plot_model(DistancePrevReward) +
  font_size(title=2) +
  theme_sjplot() 

pCoeffs

```
